Discrete Quantum Theories and Computing

### 2018-04-11 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

When we check the compatibility between quantum mechanics and computer
science, we found their fundamental assumptions are different. On
one hand, the quantum theory is based on infinitely precise real and
complex numbers. Although its predicting ability to quantum phenomenon
is limited by measurement precision, it can well describe the physical
reality together with error analysis. On the other hand, current computers
perform digital computation most of the time, except some analog chips
communicating with physical world~\cite{Camenzind2005}. While the
computability of digital parts is faithfully characterized by its
theoretical model, the Turing machine~\cite{Turing_1937}, the computability
of analog chips in reality is far weaker than the theoretical prediction
of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
One of the reason behind this gap is that our measurement precision
is always finite, and some of the difference cannot be compensated
by error analysis technique. All these problems for classical computation
could potentially apply to quantum computation. To address these issues,
we tried to develop two different types of quantum theories and computing.
Since classical discrete computing model faithfully represents digital
computers, we first tried to build discrete quantum theories and computing
by considering quantum theories and computing over finite fields in
Chapter~\ref{chap:DQT=000026DQC}. In order to , We then tried to
incorporate the idea of finite precision measurement with quantum
theories in Chapter~\ref{chap:QIVPM}.

\chapter{Conventional Quantum Theory}

>>>>

When we check the compatibility between quantum mechanics and computer
science, we found their fundamental assumptions are different. On
one hand, the quantum theory is based on infinitely precise real and
complex numbers. Its prediction could fit the physical reality by
utilizing error analysis technique although these prediction cannot
be completely faithful because of the measurement precision. On the
other hand, current computers mostly perform digital computation,
except some analog chips communicating with physical world~\cite{Camenzind2005}.
While the computability of digital parts is faithfully characterized
by its theoretical model, the Turing machine~\cite{Turing_1937},
the computability of analog chips in reality is far weaker than the
theoretical prediction of real computation \cite{Siegelmann1998,Ziegler2007,weihrauch2012computable,blum2012complexity}.
One of the reason behind this gap is also due to measurement precision,
and some of their computability difference cannot be compensated by
error analysis technique. All these problems for classical computation
could potentially apply to quantum computation. Because we are agnostic
about whether the physical reality is ultimately discrete or continuous,
we tried to develop two different types of quantum theories and computing
models to address these issues. Since the discrete classical computing
model faithfully represents digital computers, we first tried to build
discrete quantum theories and computing by considering quantum theories
and computing over finite fields in Chapter~\ref{chap:DQT=000026DQC}.
Since error analysis technique cannot always compensate the inevitable
problem of measurement precision, we then incorporate the idea of
finite precision measurement into the quantum theory in Chapter~\ref{chap:QIVPM},
and hope it could describe the physical reality and computability
more faithful.

\chapter{Conventional Quantum Theory and Computing}
